Nonlinear system identification using machine learning tools

### 2021-03-25 sysID.tex
OK, will do one more hybrid model.

\section{Large, CSTR and flash system example}
We next study the performance of the black-box NN modeling framework on a large chemical process that consists of a chemical reactor and flash separator in series. The process is depicted in Figure \ref{fig:cstr_flash}, and the ordinary differential equations (ODEs) with parameter values describing the plant model are shown in Appendix \ref{app:cstr_flash}.

\begin{figure}[!h]
  \centering
  \includegraphics[page=1, height=0.3\textheight,
                   width=0.6\textwidth]{cstr_flash.pdf}
  \caption{Schematic of the CSTR and flash chemical process.}
  \label{fig:cstr_flash}
\end{figure}

@@

@@

\begin{align*}
  \dfrac{dH_r}{dt} &= \dfrac{F + D -F_r}{A_r}\\
  \dfrac{dC_{Ar}}{dt} &= \dfrac{F(C_{Af} -C_{Ar}) +
                         D(C_{Ad} -C_{Ar})}{A_rH_r} - r_1 \\
  \dfrac{dC_{Br}}{dt} &= \dfrac{-FC_{Br} + 
                          D(C_{Bd} -C_{Br})}{A_rH_r} + r_1 -3r_2\\
  \dfrac{dC_{Cr}}{dt} &= \dfrac{-FC_{Cr} + 
  D(C_{Cd} -C_{Cr})}{A_rH_r} + r_2\\
  \dfrac{dT_r}{dt} &= \dfrac{F(T_f - T_r) + D(T_d -T_r)}{A_rH_r} + 
                      \dfrac{r_1\Delta H_1 + r_2\Delta H_2}{\rho C_p} - 
                      \dfrac{Q_r}{\rho A_r C_p H_r}\\
\end{align*}

\begin{align*}
  \dfrac{dH_b}{dt} &= \dfrac{F_r - F_b - D}{A_b} \\
  \dfrac{dC_{Ab}}{dt} &= \dfrac{F_r(C_{Ar} -C_{Ab}) + 
                          D(C_{Ab} -C_{Ad})}{A_bH_b} \\
  \dfrac{dC_{Bb}}{dt} &= \dfrac{F_r(C_{Br} -C_{Bb}) + 
                          D(C_{Bb} -C_{Bd})}{A_bH_b} \\
  \dfrac{dC_{Cb}}{dt} &= \dfrac{F_r(C_{Cr} -C_{Cb}) + 
                          D(C_{Cb} -C_{Cd})}{A_bH_b} \\
  \dfrac{dT_b}{dt} &= \dfrac{F_r(T_r - T_b)}{A_bH_b} +
                      \dfrac{Q_b}{\rho A_b C_p H_b}\\
\end{align*}

@@

The parameters in this model and the control input constraints used for the optimization problems are summarized in Table \ref{table:cstr_flash_pars}.

>>>>

\section{Large, CSTR and flash system example}
We next study the performance of the black-box NN modeling framework on a large chemical process that consists of a chemical reactor and flash separator in series. The process is depicted in Figure \ref{fig:cstr_flash}, and the ordinary differential equations (ODEs) with parameter values describing the plant model are shown in Appendix \ref{app:cstr_flash}. The model consists of 12 states ($H_r$, $C_{Ar}$, $C_{Br}$, $C_{Cr}$, $T_r$, $H_b$, $C_{Ab}$, $C_{Bb}$, $C_{Cb}$, $T_b$), 6 measurements ($H_r$, $C_{Br}$, $T_r$, $H_b$, $C_{Bb}$, $T_b$), and 2 control inputs ($F$, $D$). The sample time for the measurements is 1 min.

\begin{figure}[!h]
  \centering
  \includegraphics[page=1, height=0.5\textheight,
                   width=0.7\textwidth]{cstr_flash.pdf}
  \caption{Schematic of the CSTR and flash chemical process.}
  \label{fig:cstr_flash}
\end{figure}

@@

% \begin{figure}[!h]
%   \centering
%   \includegraphics[page=1, height=0.5\textheight,
%                    width=0.7\textwidth]{cstr_flash_plots.pdf}
%   \caption{Schematic of the CSTR and flash chemical process.}
%   \label{fig:cstr_flash_uvalidation}
% \end{figure}

% \begin{figure}[!h]
%   \centering
%   \includegraphics[page=2, height=0.5\textheight,
%                    width=0.7\textwidth]{cstr_flash_plots.pdf}
%   \caption{Schematic of the CSTR and flash chemical process.}
%   \label{fig:cstr_flash_yvalidation}
% \end{figure}

@@

\begin{align*}
  \dfrac{dH_r}{dt} &= \dfrac{F + D -F_r}{A_r}\\
  \dfrac{dC_{Ar}}{dt} &= \dfrac{F(C_{Af} -C_{Ar}) +
                         D(C_{Ad} -C_{Ar})}{A_rH_r} - r_1 \\
  \dfrac{dC_{Br}}{dt} &= \dfrac{-FC_{Br} + 
                          D(C_{Bd} -C_{Br})}{A_rH_r} + r_1 -3r_2\\
  \dfrac{dC_{Cr}}{dt} &= \dfrac{-FC_{Cr} + 
  D(C_{Cd} -C_{Cr})}{A_rH_r} + r_2\\
  \dfrac{dT_r}{dt} &= \dfrac{F(T_f - T_r) + D(T_d -T_r)}{A_rH_r} + 
                      \dfrac{r_1\Delta H_1 + r_2\Delta H_2}{\rho C_p} - 
                      \dfrac{Q_r}{\rho A_r C_p H_r}\\
  \dfrac{dH_b}{dt} &= \dfrac{F_r - F_b - D}{A_b} \\
  \dfrac{dC_{Ab}}{dt} &= \dfrac{F_r(C_{Ar} -C_{Ab}) + 
                          D(C_{Ab} -C_{Ad})}{A_bH_b} \\
  \dfrac{dC_{Bb}}{dt} &= \dfrac{F_r(C_{Br} -C_{Bb}) + 
                          D(C_{Bb} -C_{Bd})}{A_bH_b} \\
  \dfrac{dC_{Cb}}{dt} &= \dfrac{F_r(C_{Cr} -C_{Cb}) + 
                          D(C_{Cb} -C_{Cd})}{A_bH_b} \\
  \dfrac{dT_b}{dt} &= \dfrac{F_r(T_r - T_b)}{A_bH_b} +
                      \dfrac{Q_b}{\rho A_b C_p H_b}\\
\end{align*}

@@

The parameters used to simulate the model and the control input constraints used for the optimization problems are summarized in Table \ref{table:cstr_flash_pars}.

\newpage
